\Title

### 2023-07-12 Grimaldi-etal-BiolCybernetics.tex
conv_HD-SNN

        In response to an instance of the event-based input (Left), we show the neural activity of the HD-SNN model (Right). For visualization purposes, we show only one spatio-temporal slice for a given vertical position ($y = 32$), for a quarter of horizontal positions. The input spiking activity consists of ON and OFF spikes (as in~\seeFig{motion_task}) and illustrates the switching of the naturalistic event-based stream from one motion to another. The output activity consists of an analog component corresponding to the evidence accumulated by the model on the spatio-temporal kernels, and a spiking part (overlaid on this activity as vertical bars) which corresponds to instants when this evidence is above the spiking threshold. Note that this activity is consistent with the motion of the input stream. The class of each output neuron is represented by a similar color as in \seeFig{motion_task}. Finally, an accuracy can be computed by comparing the ground truth motion in the input movie with that predicted by the model.

>>>>

        In response to an instance of the event-based input (Left), we show the neural activity of the HD-SNN model (Right). For visualization purposes, we show only one spatio-temporal slice for a given vertical position ($y = 32$), for a quarter of horizontal positions. The input spiking activity consists of ON and OFF spikes (as in~\seeFig{motion_task}) and illustrates the switching of the naturalistic event-based stream from one motion to another, as denoted by the colored dots above the graph (with the class of each output neuron is represented by a similar color as in \seeFig{motion_task}). The output activity consists of an analog component corresponding to the evidence accumulated by the model on the spatio-temporal kernels, and a spiking part (overlaid on this activity as vertical bars) which corresponds to instants when this evidence is above the spiking threshold. Note that this activity is consistent with the motion of the input stream. Finally, an accuracy can be computed by comparing the ground truth motion in the input movie with that predicted by the model.
